---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gavir

<!-- badges: start -->
<!-- badges: end -->

This package is a suite of helper functions that can be used at Gavi. It has functions to help simplify repeat procedures, like loading common data, gavi specific colors and themes for plots and tables, and functions which add and filter common varibles like country groupings and iso3 codes. 

## Installation

You can install the development version of gavir from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joshualorin/gavir")
```

## Examples 

You can use the `get_*()` functions to load data:

```{r load_data}
library(gavir)
library(tidyverse, warn.conflicts = F, verbose = F)

# all functions require a version date
get_groupings("2023-07")

# and most have additional parameters you can fiddle with
get_ihme("2023-02", source = "subnational", vaccine = "dtp3")

```


`theme_*()` and `scale_*()` functions allow for standard gavi formatting and colors:

```{r plot}

wuenic %>%
 filter(iso3 == "AFG" & vaccine %in% c("dtp1", "dtp3")) %>%
 ggplot(aes(year, coverage, color = vaccine)) +
 geom_line() +
 geom_point() +
 scale_color_gavi() + 
 theme_gavi()

```

